


Data synthesis for group project data.


```{r}
library(synthpop)
library(tidyverse)
```



```{r}
#create data frame with raw data from google analytics
ga_data_raw <- read_csv("ga_data_raw.csv")
```



```{r}
#Synthesize

#choosing which variables we want to synthesize. For example, we exclude date from the synthesis as we want those to be the same as in the original data frame.

ga_data_syn <- syn(ga_data_raw, visit.sequence = c("sessions", "users", "goal2Completions", "goal3Completions", "goal5Completions", "goal9Completions"))
```

```{r}
#extract the dataset into a data frame

synthesized_ga_data <- ga_data_syn$syn

```


```{r}
#compare statistics

summary(ga_data_raw)
summary(synthesized_ga_data)
```

```{r}
#plot the comparisons
#use console to press return for each plot when prompted (during loading)
compare(ga_data_syn, ga_data_raw)
```


```{r}
#plot 2 different graphs to compare raw vs synthesized data
ggplot(ga_data_raw, aes(date, goal9Completions)) + 
         geom_line() 
```


```{r}
ggplot(synthesized_ga_data, aes(date, goal9Completions)) + 
         geom_line()
```


```{r}
#as you can see, the data has been synthesized successfully as we can see different values, especially the ones above a value of 1.

###

#export to csv (then rename "api_call_data_wrangle" to "data_wrangle" as you are no longer doing an api call). Then replace the api call in the data_wrangle file (as seen below) with a read_csv line.

###

# ga_data <- google_analytics(my_ga_id, 
#                            date_range = c("2019-01-01", today()), 
#                            metrics = c("sessions",
#                                        "users", 
#                                        "goal2Completions",
#                                        "goal3Completions", 
#                                        "goal5Completions", 
#                                        "goal9Completions"), 
#                            dimensions = c("date", "latitude", "longitude", "city"), 
#                            anti_sample = TRUE)

#also delete the following lines 

# ga_auth()

#Get a list of accounts you have access to
#account_list <- ga_account_list()


#Select the one you want to work with
#my_ga_id <- 102407343

###

#remove ga_data_final.csv from the project folder you created as you no longer need it and you don't want to upload that to github as it has original data.

write_csv(synthesized_ga_data, "synthesized_ga_data.csv")

```


You should now have a new folder called something like "dashboard_project" and initialise it as a new git repo. Make sure you don't put the folder in another one which has already been initialised as a git repo.


The folder should have the following docs:

- r project
- data_wrangle (previous api_call_data_wrangle)
- synthesized_ga_data
- server
- ui













